\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-07 related-work.tex
Boite

\noindentparagraph{\`A la carte.}

@@

Our approach addresses the expression problem by extending the
linguistic facilities offered by a proof assistant.
Families, in particular, offer an organizational advantage.  They allow
grouping and coevolving related types, functions, and proofs without
explicit parameterization;
all further-bindable fields and all opaque fields are automatically
extensibility hooks.
Because family polymorphism does not require explicit parameterization
or complex encodings,
the resulting programming experience and code are accessible to the
working Coq programmer.
The more OO aspects of family polymorphism, such as the ability to
override and families as mixins, also facilitate extensibility and reuse
with minimal programmer effort.

>>>>

\noindentparagraph{Encodings based on product lines or DTC.}

\citet{delaware2011} engineer product lines of theorems and proofs built
from feature modules. Feature composition is manual, which seems to have
motivated later approaches based on DTC.

@@

Our approach addresses the expression problem by extending the
linguistic facilities offered by a proof assistant.
Families, in particular, offer an organizational advantage.  They allow
grouping and coevolving related types, functions, and proofs without
explicit parameterization;
all further-bindable fields are automatically extensibility hooks.
Because family polymorphism does not require explicit parameterization
or complex encodings,
the resulting programming experience and code are accessible to the
working Coq programmer.
The more OO aspects of family polymorphism, such as the ability to
override and families as mixins, also facilitate extensibility and reuse
with minimal programmer effort.

\noindentparagraph{Proof reuse, proof weaving, and proof repair.}

\citet{boite2004proof} addresses proof reuse specifically in response
to inductive types extended with new constructors. Proof reuse is
via a tactic that adapts the original proof to the extended inductive
type while generating proof obligations, so rechecking of proof terms is
entailed.
The design requires distinct names for a base inductive type and its
extensions (including distinct names for constructors), while our
approach supports the late binding of names.
